---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tenupR

<!-- badges: start -->
[![R-CMD-check](https://github.com/MathieuGenu/tenupR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/MathieuGenu/tenupR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

{tenupR} is an R package allowing to compute ranking of a tennis player, playing in the french league. This is possible by giving :

- matches records of a player with a specific format
- ranking to test
- date of simulation

Note : Ranking is possible from NC to -15

## Installation

You can install the development version of tenupR like so:


```{r eval=FALSE}
install.packages("remotes")
remotes::install_github("MathieuGenu/tenupR")
```


## Example

IN PREP. :construction:


## TO DO

- [ ] Hex logo
- [ ] Add the fact that you should at least win against one opponent of the same / over ranking you are testing
- [ ] Down-ranking occurs once per year-on-year if not enough points to validate current ranking
- [ ] in 2nd series (negative an positive), if V-E-2I-5G <= -100 down-ranking
- [ ]
